PM Mungbean meta-analysis

### 2020-06-08 02_Preliminary_analysis.Rmd
corrections

The data explored in the `PM_MB_means` data frame is a list of mean values from each treatment in each respective experiment.
These preliminary analyses will focus on the change in mungbean yields which is attributable to the fungicide treatment. 
Later in this document we will also consider the impact of fungicide treatments on disease incidence/severity. 
Mean powdery mildew incidence was recorded at the end of each growing season. 
Some experiments recorded disease incidence throughout the season and these were summarised with AUDPC. 
AUDPC for trials which only provided final powdery mildew incidence was calculated using the record of 'first sign of disease' and final assessment. 
More details on how the `PM_MB_means` data was compiled can be found in the ['Data wrangle vingette'][./vignette/191115_PMMB_DataWrangling_PM.Rmd]

Various factors have been studied in the previous experiments which may influence the subsequent meta-analysis.
On this page, unless stated, the following plots and analyses were made disregarding effects the following factors which have the potential to influence mungbean grain yield and/or powdery mildew mean plot severity.

@@

The data plotted below are from `r length(unique(PM_MB_means$trial_ref))` field trials between (`r first(levels(PM_MB_means$year))` - `r last(levels(PM_MB_means$year))`) of which the details are described in [Studies considered in meta-analysis section](#studies-considered-in-meta-analysis).

@@

The demethylation inhibitors (DMI), tebuconazole and propiconazole, are used in included in the highest frequencies, along with sulphur. The DMIs have the same fungicide mode of action and are good candidates to be pooled in the meta-analysis.

@@

```{r Fungicide_x_nSprays_tble2, message=FALSE}
PM_MB_means %>%
   group_by(fungicide_ai, total_fungicide) %>%
   summarise(
      n = length(prop_YG),
      lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
      median = median(prop_YG, na.rm = T),
      mean = mean(prop_YG, na.rm = T),
      upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))
   ) %>%
   filter(n >= 5) %>% # remove any fungicide groups with less than 5 observations
   arrange(desc(median)) %>%
   kable(caption = "Fungicide effect on proportion of yield gain.",
         col.names = c("Fungicide active ingredient", "Total fungicide applications","*n* Treatments","Lower 2.5% quartile","Median proportional grain yield", "Mean proportional grain yield","97.5 % quartile")) %>%
   kable_styling(fixed_thead = T, full_width = T) %>%
   footnote(general = "Fungicides with less than five observations were omitted from this table")
```

@@

```{r Fungicide_x_nSprays_tble1, message=FALSE}

>>>>

The data explored in the `PM_MB_means` data frame is a list of mean values from each treatment in each respective experiment.
These preliminary analyses will focus on the change in mungbean yields which is attributable to the fungicide treatment. 
Later in this document we will also consider the impact of fungicide treatments on disease incidence/severity. 
Mean powdery mildew incidence was recorded at the end of each growing season. 
Some experiments recorded disease incidence throughout the season and these were summarised with AUDPC. 
AUDPC for trials which only provided final powdery mildew incidence was calculated using the record of 'first sign of disease' and final assessment. 
More details on how the `PM_MB_means` data was compiled can be found in the ['Data wrangle vingette'](./vignette/191115_PMMB_DataWrangling_PM.html)

Various factors have been studied in the previous experiments which may influence the subsequent meta-analysis.
On this page, unless stated, the following plots and analyses were made disregarding other effects.
The following factors are propostulated to potentially influence mungbean grain yield and/or powdery mildew mean plot severity.

@@

The data plotted below are from `r length(unique(PM_MB_means$trial_ref))` field trials between (`r first(levels(PM_MB_means$year))` - `r last(levels(PM_MB_means$year))`) of which the details are described in the [studies considered in meta-analysis section](#studies-considered-in-meta-analysis).

@@

The demethylation inhibitors (DMI), tebuconazole and propiconazole, are used in the highest frequencies, along with sulphur. The DMIs have the same fungicide mode of action and are good candidates to be pooled in the meta-analysis.

@@

```{r Fungicide_x_nSprays_tble2, message=FALSE}
PM_MB_means %>%
   group_by(fungicide_ai, total_fungicide) %>%
   summarise(
      n = length(prop_YG),
      lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
      median = median(prop_YG, na.rm = T),
      mean = mean(prop_YG, na.rm = T),
      upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))
   ) %>%
   filter(n >= 5) %>% # remove any fungicide groups with less than 5 observations
   arrange(desc(median)) %>%
   kable(caption = "Fungicide effect on proportion of yield gain.",
         col.names = c("Fungicide active ingredient", "Total fungicide applications","n Treatments"," 2.5% quartile","Median proportional grain yield", "Mean proportional grain yield","97.5 % quartile")) %>%
   kable_styling(fixed_thead = T, full_width = T) %>%
   footnote(general = "Fungicides with less than five observations were omitted from this table")

PM_MB_means[PM_MB_means$location == "Wellcamp",]
```

@@

```{r Fungicide_x_nSprays_tble1, message=FALSE, warning=FALSE}
